### 2012-09-22 sermons/Luke9:23-26.tex
M.

\subsection{The disciple's treasure}
\I  Now you may be wondering where the good news is,
        and it is in verse 24.
\Q{ For whoever desires to save his life will lose it,
    but whoever loses his life for My sake will save it.}
\I  ``For'' means that Jesus is explaining the previous verse.
    He is giving the principle that undergirds verse 23.
\I  He explains this principle from both a negative and positive
        perspective.
\I  Jesus starts with the negative,
    ``For whoever desires to save his life will lose it,''
\BI \I  This is the one who was unwilling to surrender his life 
            to serve Jesus.
    \I  Instead, he desired to save it, 
    \EI

\I  Note that no one can actually save their own life, 
        they can only desire/attempt to.

\I  It must be for His sake!

\subsection{The reasoning}
For what profit is it to a man if he gains the whole world,
    and is himself destroyed or lost?
\I  We sacrifice only what we would inevitably lose anyways. 
    We make no \emph{true} sacrifice.

For whoever is ashamed of Me and My words,
    of him the Son of Man will be ashamed when He comes in His own glory,
    and in His Father's, and of the holy angels.

\section{The power of brotherly love}

>>>>

\subsection{The disciple's treasure}
\I  Now you may be wondering where the good news is,
        and it is in verse 24.
\Q{ For whoever desires to save his life will lose it,
    but whoever loses his life for My sake will save it.}
\I  ``For'' means that Jesus is explaining the previous verse.
    He is giving the principle that undergirds verse 23.
\I  He explains this principle from both a negative and positive
        perspective.

\I  Jesus starts with the negative,
    ``For whoever desires to save his life will lose it,\ldots''
\BI \I  Here, Jesus describes the one who, 
            upon hearing the terms of discipleship,
            no longer desires to be His disciple.
    \I  He is unwilling to surrender his life to serve Jesus.
    \I  Instead, this one desires to save his life.
    \BI \I  To use his time to pursue his own goals and to do his own will. 
        \I  Note the vanity of such a pursuit, that he cannot succeed in it,
                but he can only \emph{desire} to save his life. \EI
    \I  Instead, his end is that he loses the very life 
            he was attempting to save.
    \BI \I  Everything he gathered in this life is scattered upon his death, and
        \I  he now experiences eternal judgement in hell. \EI
    \EI

\I  Jesus then explains the positive, 
        ``\dots but whoever loses his life for My sake will save it.''
\BI \I  This is the one who agrees to Jesus' terms of unconditional 
            surrender and unconditional service.
    \I  He loses his life because he has denied himself and 
            has instead taken up a cross.
    \BI \I  He may no longer please himself, or
                even decide how to live.
        \I  However, note that he has not simply thrown his life away,
                but he has lost if \emph{for Jesus' sake}. \EI  
    \I  His outcome is salvation and eternal life. \EI

\I  This answers the question of why someone would
\BI \I  deny themselves,
    \I  take up their cross, and
    \I  lose their lives, \EI
    to follow Jesus.

\I  It is all in order to gain eternal life!
\BI \I  In fact, their sacrifice was never truly a sacrifice
            because of the surpassing value of the treasure
            they received in return. \EI

\I  Was this not true of you?
\BI \I  At the point of your salvation,
            what drove you to renounce all that you were,
            and to submissively commit yourself to all that Jesus
            would have for you?
    \I  Was it not because you were overwhelmed by the value of
            salvation, so that your loss seemed very small indeed?
    \I  Were you not willing, because of the riches of the treasure,
            to part with all that you had in order to obtain it? \EI

\I  The believer is empowered to deny himself by
        beholding the surpassing riches of God's promised blessing.
\BI \I  It is the greatness, extravagance, and sureness,
            of God's promise that empowers the believer to
            follow and obey! \EI

\I  And if so at the moment of salvation,
        should not it be ever more so after salvation?

\section{The power to love}
\I  Yes! Just as the power to deny ourselves and take up our cross was in
        the promise of eternal life,
        so the power to deny ourselves and obediently love one another now
        lies in \emph{the promise of eternal life now}.

\I  Remember, eternal life is not simply living forever, it is fellowship with God.
\BI \I John 17:3
        \Q{ And this is eternal life, that they may know You, 
            the only true God, and Jesus Christ whom You have sent.} 
    \I  Heaven is knowing God without any sin in the way! \EI

\I  Therefore, what empowers a believer unto obedience is 
        the blessing of a deeper and fuller communion with God.
\BI \I  Or, the believer obeys in order to 
            more richly experience eternal life \emph{now}. \EI

\I  Philippians 3:8
    \Q{ Yet indeed I also count all things loss for the excellence
            of the knowledge of Christ Jesus my Lord,
            and count them as rubbish, that I may gain Christ \ldots}
